---
title: "Tests of known OSM ways"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tests of known OSM ways}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(osmactive)
library(dplyr)
# devtools::load_all() # for development
```

The following test checks to see if a known OSM way in Leeds, a footpath in Leeds in a path on which cycling is allowed and is common, is correctly identified, as Shared Use.

```{r}
osm = get_travel_network("Leeds")
potternewton_path = osm |>
  filter(osm_id == 306849934)
cycle_net = get_cycling_network(potternewton_path)
nrow(cycle_net)
drive_net = get_driving_network(osm)
cycle_net = distance_to_road(cycle_net, drive_net)
cycle_net_classified = classify_cycle_infrastructure(cycle_net)
cycle_net_classified |>
  pull(cycle_segregation)
```

Let's check out 'highway=path' tagged segments in the network in Leeds:

```{r}
cycle_net = get_cycling_network(osm)
cycle_net = distance_to_road(cycle_net, drive_net)
cycle_net = classify_cycle_infrastructure(cycle_net)
tmap::tmap_mode("view")
cycle_net_path = cycle_net |>
  filter(highway == "path")
m = plot_osm_tmap(cycle_net_path)
m
# tmap::tmap_save(m, "path.html")
# browseURL("path.html")
```

Leith Walk, should be Segregated Track (narrow).
It is on part of it, with the following tags for way [22587411](https://www.openstreetmap.org/way/22587411).

```{r}
osm = get_travel_network("Edinburgh", force_download = TRUE)
nrow(osm)
sum(osm$cycleway_left == "separate", na.rm = TRUE)
# Full cycle network:
cycle_net = get_cycling_network(osm)
nrow(cycle_net)
table(cycle_net$cycleway_right)
drive_net = get_driving_network(osm)
cycle_net = distance_to_road(cycle_net, drive_net)
cycle_net = classify_cycle_infrastructure(cycle_net)
m = plot_osm_tmap(cycle_net)
tmap::tmap_save(m, "leith_walk_full.html")
browseURL("leith_walk_full.html")
```

```{r}
leith_walk_narrow = cycle_net |>
  filter(osm_id == 1209807764)
get_cycling_network(leith_walk_narrow)
leith_walk_narrow_minimal = leith_walk_narrow |>
  select_if(~ !all(is.na(.))) |>
  sf::st_drop_geometry()
leith_walk_narrow_minimal
```

```{r, echo=FALSE}
#       osm_id  highway oneway                            cycleway_chars lit
# 1 1209807764 cycleway    yes NA|NA|NA|NA|NA|NA|NA|NA|NA|NA|NA|NA|NA|NA yes
#   width surface smoothness z_order distance_to_road detailed_segregation
# 1     1 asphalt       good       0              9.1          Level track
#   cycle_pedestrian_separation width_clean         cycle_segregation
# 1                     Unknown           1 Segregated Track (narrow)
```

Another part of the same corridor, way 1214008544, is classified as Shared Footway: 

```{r}
leith_walk_footway = cycle_net |>
  filter(osm_id == 1214008544)
leith_walk_footway_minimal = leith_walk_footway |>
  select_if(~ !all(is.na(.))) |>
  sf::st_drop_geometry()
leith_walk_footway_minimal
```

```{r, echo=FALSE}
#      osm_id       name highway maxspeed oneway cycleway_left cycleway_right lit
# 1 578114866 Leith Walk primary   20 mph    yes      separate             no yes
#   surface z_order
# 1 asphalt       7
#                                                                                       other_tags
# 1 "name:left"=>"Crighton Place","ref"=>"A900","sidewalk:left"=>"separate","sidewalk:right"=>"no"
```

Let's compare them:

```{r}
waldo::compare(leith_walk_narrow, leith_walk_footway)
```

Highway=path should be

```{r}
leith_walk = osm |>
  filter(name == "Leith Walk")
cycle_net = get_cycling_network(leith_walk)
drive_net = get_driving_network(osm)
cycle_net = distance_to_road(cycle_net, drive_net)
cycle_net = classify_cycle_infrastructure(cycle_net)
cycle_net |>
  pull(cycle_segregation)
m = plot_osm_tmap(cycle_net)
m
```

```{r}
tmap::tmap_save(m, "leith_walk.html")
browseURL("leith_walk.html")
```

# 757849580

```{r}
cloch_lighthouse = zonebuilder::zb_zone("Cloch Lighthouse", n_circles = 3)
cloch_lighthouse_union = sf::st_union(cloch_lighthouse)
osm = get_travel_network("Scotland", boundary = cloch_lighthouse_union, boundary_type = "clipsrc")
osm_cloch_road = osm |>
  filter(osm_id == 757849580)
osm_cloch_road_1km = osm_cloch_road |>
  sf::st_buffer(1000)
osm_cloch_road_1km = osm |>
  sf::st_intersection(osm_cloch_road_1km)
plot(osm_cloch_road_1km$geometry)
mapview::mapview(osm_cloch_road_1km)
cycle_net = get_cycling_network(osm_cloch_road_1km)
drive_net = get_driving_network(osm_cloch_road_1km)
cycle_net = distance_to_road(cycle_net, drive_net)
cycle_net = classify_cycle_infrastructure(cycle_net)
# # # Make changes to osmactive code then reload with
devtools::load_all()
# osm_classified_coch = osm_classified |>
#   filter(osm_id == 757849580)
# # osm_classified_coch$cycle_pedestrian_separation
# # # [1] Shared Footway (not segregated)
# # # 3 Levels: Shared Footway (segregated) < ... < Unknown
# # osm_classified_coch$cycle_segregation
# osm_classified = osm_classified_coch
cycle_net_cloch_road = cycle_net |>
  filter(osm_id == 757849580)
cycle_net_cloch_road$cycle_segregation # Should be shared footway
m = plot_osm_tmap(cycle_net)
tmap::tmap_mode("view")
m
tmap::tmap_save(m, "cloch_road.html")
# Save the cycle_net
sf::write_sf(cycle_net, "cycle_net_cloch_road.geojson")
system("gh release list")
system("gh release upload v0.1 cycle_net_cloch_road.geojson cloch_road.html --clobber")
# See result online at https://github.com/nptscot/osmactive/releases/tag/v0.1/cycle_net_cloch_road.geojson
```