---
title: "Scottish Cycling by Design classification"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Scottish Cycling by Design classification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
timeout(3000)
library(osmactive)
library(tidyverse)
library(sf)
tmap::tmap_mode("view")
```

The default classification is the Cycling by Design guidance from the Scottish Government. This is a detailed classification system that includes the following categories, based on a minimal example dataset:

```{r}
osm = osm_edinburgh
cycle_net = get_cycling_network(osm)
drive_net = get_driving_network(osm)
drive_net_major = get_driving_network(osm)
cycle_net = distance_to_road(cycle_net, drive_net)
cycle_net = classify_cycle_infrastructure(cycle_net)
table(cycle_net$detailed_segregation)
table(cycle_net$cycle_segregation)
```

```{r minimal_plot_osm}
m = plot_osm_tmap(cycle_net)
m
```

Let's try running the code on a larger example, covering Edinburgh:

```{r edinburgh}
osm = get_travel_network("Edinburgh")
cycle_net = get_cycling_network(osm)
drive_net = get_driving_network(osm)
cycle_net = distance_to_road(cycle_net, drive_net)
cycle_net = classify_cycle_infrastructure(cycle_net)
central_edinburgh = osm_edinburgh |>
  sf::st_union() |>
  sf::st_centroid() |>
  sf::st_buffer(3000)
m = plot_osm_tmap(cycle_net[central_edinburgh, ])
m
```

We can pick out specific bits of infrastructure, e.g. those mentioned in issue [#67](https://github.com/nptscot/osmactive/issues/67): 

> https://www.openstreetmap.org/way/1137759929 shows up as this right now, but this looks like a narrow segregated / stepped track to me. https://www.openstreetmap.org/way/1209807768 is another case that doesn't seem like off-road.

> My idea of off-road cycleway were things like https://www.openstreetmap.org/way/7973833 and https://www.openstreetmap.org/way/265320503 -- things with no parallel road nearby.

Let's pull out those bits of infrastructure:

```{r}
cycle_net_included = cycle_net |>
  subset(osm_id %in% c(1137759929, 1209807768, 7973833, 265320503))
names(cycle_net_included)
cycle_net_included[c("osm_id", "distance_to_road", "cycle_segregation")] |>
  sf::st_drop_geometry() |>
  knitr::kable()
```

We can also plot these as follows:

```{r}
m = plot_osm_tmap(cycle_net_included)
m
```

# Level of service

The level of service associated with each link can be calculated based on the Level of Service table in the Cycling by Design guidance:

![]()

A tabular representation of this data is as follows, after translating CbD infrastructure categories into NPT categories:

```{r}
# table(cycle_net$cycle_segregation)
#   Segregated Track (wide)         Off Road Cycleway Segregated Track (narrow) 
#                       214                       973                       859 
#            Shared Footway        Painted Cycle Lane 
#                      3325                       522 
los_table = read_csv("https://github.com/nptscot/osmactive/raw/refs/heads/main/inst/extdata/level-of-service-table.csv")
# names(los_table)
#  [1] "Motor Traffic Speed (85th percentile)"
#  [2] "Speed Limit (mph)"                    
#  [3] "Two-way traffic flow (pcu per day)"   
#  [4] "Two-way traffic flow (pcu per hour)"  
#  [5] "Mixed Traffic Street"                 
#  [6] "Detached or Remote Cycle Track"       
#  [7] "Cycle Track at Carriageway Level"     
#  [8] "Stepped or Footway Level Cycle Track" 
#  [9] "Light Segregation"                    
# [10] "Cycle Lane"
table(los_table$`Two-way traffic flow (pcu per day)`)
  #  0 to 1000    0 to 2000 1000 to 2000        1000+ 2000 to 4000        2000+ 
  #          4            1            2            2            2            1 
  #      4000+          All 
  #          2            1 
los_table_npt = los_table |>
  transmute(
    `Speed (85th kph)` = `Motor Traffic Speed (85th percentile)`,
    `Speed Limit (mph)` = `Speed Limit (mph)`,
    AADT = `Two-way traffic flow (pcu per day)`,
    `Mixed Traffic Street`,
    `Off road cycleway` = `Detached or Remote Cycle Track`,
    `Segregated Track (wide)` = `Cycle Track at Carriageway Level`,
    `Segregated Track (narrow)` = `Light Segregation`
  ) |>
  # Convert the categories to "0 to 1999", "2000 to 3999", "4000+"
  mutate(
    AADT = npt_to_cbd_aadt(AADT)
  )

los_table_npt |>
  knitr::kable()
```

We can convert this table into a 'long' format for use internally.

```{r}
los_table_long = los_table_npt |>
  pivot_longer(cols = -c(`Speed (85th kph)`, `Speed Limit (mph)`, AADT),
               names_to = "infrastructure",
               values_to = "level_of_service")
los_table_long
# write_csv(los_table_long, "inst/extdata/level-of-service-table-long.csv")
usethis::use_data(los_table_long, overwrite = TRUE)
```

Next, we calculate the speed limits as follows:

```{r}
# table(los_table_long$`Speed Limit (mph)`)
# <20 mph  20 mph  30 mph  40 mph  50 mph 60+ mph 
#      12      16      12       8       8       4 
cycle_net_speeds = clean_speeds(cycle_net)
# table(cycle_net_speeds$maxspeed_clean)
#  15  20  30  40  50  60 
#   1 314 239  92   2  22
classify_speeds = function(speed_mph) {
  dplyr::case_when(
    speed_mph < 20 ~ "<20 mph",
    speed_mph < 30 ~ "20 mph",
    speed_mph < 40 ~ "30 mph",
    speed_mph < 50 ~ "40 mph",
    speed_mph < 60 ~ "50 mph",
    speed_mph >= 60 ~ "60+ mph"
  )
}
classify_speeds(30)
classify_speeds(10)
classify_speeds(NA)
```

We can then create the `Speed Limit (mph)` and `AADT` columns in the `cycle_net` object:

```{r}
cycle_net_speeds = clean_speeds(cycle_net)
cycle_net_volumes = estimate_traffic(cycle_net_speeds)
cycle_net$`Speed Limit (mph)` = classify_speeds(cycle_net_speeds$maxspeed_clean)
cycle_net$AADT = npt_to_cbd_aadt(cycle_net_volumes$assumed_volume)
class(cycle_net_volumes$assumed_volume)
table(cycle_net$`Speed Limit (mph)`)
table(cycle_net$AADT)
```



```{r}
#| eval: false
# Check for level track on York Place
# devtools::load_all()
osm_check = "1137759929"
york_place = cycle_net |>
  filter(osm_id == osm_check)
cycle_net_los = level_of_service(york_place)
library(tmap)
mapview::mapview(cycle_net_los, zcol = "Level of Service")
```