---
title: "Cycle infrastructure classification systems"
subtitle: "Comparing international 'best practice' guides and implementing them in open source software for reproducible research and data-driven active travel planning"

# For .Rmd version:
# output: rmarkdown::html_vignette
# vignette: >
#   %\VignetteIndexEntry{Typologies of cycle infrastructure}
#   %\VignetteEngine{knitr::rmarkdown}
#   %\VignetteEncoding{UTF-8}

# For .qmd version:
format: html
number-sections: true
editor: 
  markdown: 
    wrap: sentence
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(osmactive)
```

# Abstract

Transport networks are diverse and complex.
This applies to all modes of transport, but especially to 'cycle network' which, uniquely, includes infrastructure segments that can be used both motorised and non-motorised modes.
Even in places with relatively good provision of dedicated for cycling a substantial proportion of the cyclable network is also drivable, with 'fietstrase' in The Netherlands providing a classic example.
In this paper we present a typology of cycle infrastructure classification systems and guidance on *what to build where*, based on official documents from TBC countries *and their implementation in open source software*.
We find substantial differences between each classification system.
Recent efforts to provide international guidance on how to talk about and classify cycling infrastructure has impacts on policies: measuring level of separation from motor traffic, for example, enables planners to focus on infrastructure that is safe for all.
We conclude with tentative recommendations of classification systems for different use cases, with reference to our implementation in the `osmactive` package accompanies this paper.
The work presented in this paper and our experience developing the package can provide a basis for open and community-driven classification systems that are modular, reproducible and extendable for different needs.
The work provides a basis for more data-driven cycle traffic design guidance, that can co-evolve with changing policy, community and data-availability landscapes.

# Introduction

# Academic literature review

# Official classification systems

# Results

# Discussion