---
title: "Scottish Cycling by Design classification"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Scottish Cycling by Design classification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(osmactive)
library(sf)
tmap::tmap_mode("view")
```

The default classification is the Cycling by Design guidance from the Scottish Government. This is a detailed classification system that includes the following categories, based on a minimal example dataset:

```{r}
osm = osm_edinburgh
cycle_net = get_cycling_network(osm)
drive_net = get_driving_network(osm)
drive_net_major = get_driving_network(osm)
cycle_net = distance_to_road(cycle_net, drive_net)
cycle_net = classify_cycle_infrastructure(cycle_net)
table(cycle_net$detailed_segregation)
table(cycle_net$cycle_segregation)
```

```{r minimal_plot_osm}
m = plot_osm_tmap(cycle_net)
m
```

Let's try running the code on a larger example, covering Edinburgh:

```{r edinburgh}
osm = get_travel_network("Edinburgh")
cycle_net = get_cycling_network(osm)
drive_net = get_driving_network(osm)
cycle_net = distance_to_road(cycle_net, drive_net)
cycle_net = classify_cycle_infrastructure(cycle_net)
m = plot_osm_tmap(cycle_net)
# m
```

We can pick out specific bits of infrastructure, e.g. those mentioned in issue [#67](https://github.com/nptscot/osmactive/issues/67): 

> https://www.openstreetmap.org/way/1137759929 shows up as this right now, but this looks like a narrow segregated / stepped track to me. https://www.openstreetmap.org/way/1209807768 is another case that doesn't seem like off-road.

> My idea of off-road cycleway were things like https://www.openstreetmap.org/way/7973833 and https://www.openstreetmap.org/way/265320503 -- things with no parallel road nearby.

Let's pull out those bits of infrastructure:

```{r}
cycle_net_included = cycle_net |>
  subset(osm_id %in% c(1137759929, 1209807768, 7973833, 265320503))
names(cycle_net_included)
cycle_net_included[c("osm_id", "distance_to_road", "cycle_segregation")] |>
  sf::st_drop_geometry() |>
  knitr::kable()
```

We can also plot these as follows:

```{r}
m = plot_osm_tmap(cycle_net_included)
m
```